---
title: "Study 2"
output: html_document
---

```{r setup, include=FALSE}
library("Rmisc")
library("plyr")
library("lattice")
library("ggplot2")
library("ggpubr")
library("plotrix")
library("rtdists")
library("tidyverse")
library("tidyr")
library("afex")
library("emmeans")
library("viridis")
library("cowplot")
library("stringr")
library("caret")
library("cowplot")
library("knitr")
library("lattice")
library("gsubfn") 
library("stringi")    
library("nlme")
library("Matrix")
library("writexl")
library("xlsx")
library("PairedData")
library(ggplot2) 
library(yarrr)       
library(tidyverse)
library(plotrix)      
library(knitr)        
library(kableExtra)
library(here)         
here::here()
library(psycho)
library("dplyr")
library("MOTE")
library("pwr")
library("ggbeeswarm")

theme_apa <- function(base_size = 12, base_family = "", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(
      plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0), hjust = 0.5)
      , plot.subtitle = ggplot2::element_text(size = ggplot2::rel(0.8), margin = ggplot2::margin(ggplot2::rel(-7), 0, ggplot2::rel(14), 0), hjust = 0.5)

      # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
      , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
      , axis.title.x.top = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(12), 0))
      , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
      , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
      , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
      , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
      , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
      , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
      , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
      , axis.line = ggplot2::element_line()
      # , axis.line.x = ggplot2::element_line()
      # , axis.line.y = ggplot2::element_line()

      , legend.title = ggplot2::element_text()
      , legend.key = ggplot2::element_rect(fill = NA, color = NA)
      , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.margin = ggplot2::margin(
        t = ggplot2::rel(16)
        , r = ggplot2::rel(16)
        , b = ggplot2::rel(16)
        , l = ggplot2::rel(16)
        , unit = "points"
      )

      , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
      , panel.grid.major.x = ggplot2::element_blank()
      , panel.grid.minor.x = ggplot2::element_blank()
      , panel.grid.major.y = ggplot2::element_blank()
      , panel.grid.minor.y = ggplot2::element_blank()

      , strip.background = ggplot2::element_rect(fill = NA, color = NA)
      , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
      , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )

  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }

  adapted_theme
}
```

## Data pre-processing

```{r cars}
E2dt<-read.csv("E2dt.csv",header=TRUE)
responseArray<- read.csv("responseArrayupdated.csv",header = TRUE) 
E2dt_derandomize<-read.csv("E2dt_derandomize.csv",header=TRUE)

#add response id and condition to responseArray 
responseArray$Respond.ID<-E2dt_derandomize$ResponseId
responseArray$condition<-E2dt_derandomize$condition

#remove the column of r-mean
responseArray<-responseArray[,-81]

#make response array have the same columns like e2dt
responseArray[,83:87]<-E2dt[,4:8]

responseArray$Duration..in.seconds.<-E2dt$Duration..in.seconds. #column 88

responseArray[,89:107]<-E2dt[,89:107]

#put respond.id ... in the start 
responseArray<-responseArray[,c(88,81,82,83,84,85,86,87,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73,74,75,76,77,78,79,80,89,90,91,92,93,94,95,96,97,98,99,100,101,102,103,104,105,106,107)]

E2dt<-responseArray

E2dt[E2dt$condition=="All True ","condition"] <- "All True"
E2dt[E2dt$condition=="More Fake ","condition"] <- "More Fake"
```

## Research question 1: investigate if and how differential exposure to misinformation affects individuals’ truth relativism towards true news
```{r pressure, echo=FALSE}
E2dt<-E2dt %>%
  group_by(Respond.ID) %>%
    summarize(tr80 = mean(c(X.1,          X.2 ,         X.3,          X.4,         
X.5 ,    X.6,     X.7 ,        X.8 ,         X.9 ,         X.10 ,    X.11,    
X.12 ,        X.13,         X.14,         X.15 ,   X.16,        X.17  ,       X.18  ,      
X.19  ,   X.20,   X.21 ,        X.22 ,        X.23 ,        X.24,X.25,X.26,X.27,X.28,X.29,X.30,X.31,X.32,X.33,X.34,X.35,X.36,X.37,X.38,X.39,X.40,X.41,X.42,X.43,X.44,X.45,X.46,X.47,X.48,X.49,X.50,X.51,X.52,X.53,X.54,X.55,X.56,X.57,X.58,X.59,X.60,X.61,X.62,X.63,X.64,X.65,X.66,X.67,X.68,X.69,X.70,X.71,X.72,X.73,X.74,X.75,X.76,X.77,X.78,X.79,X.80))) %>%
inner_join(E2dt, by = 'Respond.ID')

E2dt<-E2dt %>%
  group_by(Respond.ID) %>%
    summarize(trfirst8 = mean(c(X.1,          X.2 ,         X.3,          X.4,         
X.5 ,    X.6,     X.7 ,        X.8))) %>%
inner_join(E2dt, by = 'Respond.ID')

E2dt<-E2dt %>%
  group_by(Respond.ID) %>%
    summarize(trlast8 = mean(c(X.73,X.74,X.75,X.76,X.77,X.78,X.79,X.80))) %>%
inner_join(E2dt, by = 'Respond.ID')

E2dt<-E2dt %>%
  group_by(Respond.ID) %>%
    summarize(trMiddle = mean(c(X.9 ,         X.10 ,    X.11,    
X.12 ,        X.13,         X.14,         X.15 ,   X.16,        X.17  ,       X.18  ,      
X.19  ,   X.20,   X.21 ,        X.22 ,        X.23 ,        X.24,X.25,X.26,X.27,X.28,X.29,X.30,X.31,X.32,X.33,X.34,X.35,X.36,X.37,X.38,X.39,X.40,X.41,X.42,X.43,X.44,X.45,X.46,X.47,X.48,X.49,X.50,X.51,X.52,X.53,X.54,X.55,X.56,X.57,X.58,X.59,X.60,X.61,X.62,X.63,X.64,X.65,X.66,X.67,X.68,X.69,X.70,X.71,X.72))) %>%
inner_join(E2dt, by = 'Respond.ID')

## duration test
hist(E2dt$Duration..in.seconds.,50)

E2dur <- subset(E2dt, E2dt$Duration..in.seconds. < 10000)

hist(E2dur$Duration..in.seconds.,50)

summaryFN <- E2dur%>% 
                    summarySE(measurevar="Duration..in.seconds.", 
                    groupvars ="condition", na.rm=T) 
summaryFN

#ANOVAs
#between groups 
m802<-aov_ez("Respond.ID","tr80",E2dur,between = "condition")
m802
summary(m802)

afex_plot(m802,"condition",error = "between",mapping = "color")

tr_s2<-emmeans(m802,"condition")
tr_s2

tr_s2%>%
  pairs(adjust="holm")

#Anova for first 8
mf82<-aov_ez("Respond.ID","trfirst8",E2dur,between = "condition")
mf82

m1<-filter(E2dur,condition=="More Fake")
m2<-filter(E2dur,condition=="All True")

#Anova for last 8
ml82<-aov_ez("Respond.ID","trlast8",E2dur,between = "condition")
ml82

afex_plot(ml82,"condition",error = "between",mapping = "color")

tr_s2_l8<-emmeans(ml82,"condition")
tr_s2_l8

tr_s2_l8%>%
  pairs(adjust="holm")

anova_model_e2tr = lm(formula = trlast8 ~ condition, data = E2dur)
summary.aov(anova_model_e2tr)

eta.full.SS(dfm = 1, dfe = 77, ssm = 0.0994,
            sst = (0.0994+1.6072), Fvalue = 4.76, a = .05)

#Anova middle 64
ml642<-aov_ez("Respond.ID","trMiddle",E2dur,between = "condition")
ml642

afex_plot(ml642,"condition",error = "between",mapping = "color")

tr_s2_m64<-emmeans(ml642,"condition")
tr_s2_m64

tr_s2_m64%>%
  pairs(adjust="holm")


# Middle 64
summaryFN <- E2dt%>% 
                    summarySE(measurevar="trMiddle", 
                    groupvars ="condition", na.rm=T) 
summaryFN

##
ggplot(summaryFN, aes(x = condition, y = trMiddle))+
  geom_point() +
  geom_errorbar(aes(ymin=trMiddle-se, ymax=trMiddle+se), width=.2)  +
  labs(x="Condition", y = "Truth relativism")+
   theme_classic() 

## 
summaryFN2 <- E2dur%>% 
                    summarySE(measurevar="trlast8", 
                    groupvars ="condition", na.rm=T) 
summaryFN2

ggplot(summaryFN2, aes(x = condition, y = trlast8))+
  geom_point() +
  geom_errorbar(aes(ymin=trlast8-se, ymax=trlast8+se), width=.2)  +
  labs(x="Condition", y = "Truth relativism")+
   theme_classic() 

#follow-up tests for ANOVAs
em802<-emmeans(m802,"condition")
em802

con1<-list(true_vs_fake=c(1,-1))
contrast(em802, con1, adjust = "holm")

E2dt%>%
  group_by(condition)%>%
  summarise(mean=mean(tr80)) 

E2dt%>%
  group_by(condition)%>%
  summarise(mean=mean(trfirst8)) 

E2dt%>%
  group_by(condition)%>%
  summarise(mean=mean(trlast8)) 

eml82<-emmeans(ml82,"condition")
eml82

con2<-list(true_vs_fake=c(1,-1))
contrast(eml82, con2, adjust = "holm")

em642<-emmeans(ml642,"condition")
em642

con3<-list(true_vs_fake=c(1,-1))
contrast(em642, con3, adjust = "holm")

#Comparisons within/between
#Subset dataset
#Remove relativism values for each question and only remain tr80/trf8/trl8/id/conditions
E2dt1<-E2dur[,(1:7)]

#only remain trf8/trl8/id/conditions
E2dt1<-E2dt1[,-(5:6)]

#change trf8/trl8 into one column 
E2dt1<-E2dt1 %>%
  pivot_longer(c(3,4), names_to = "sequence", values_to = "trtrue")

#mixed anova \
m<-aov_ez("Respond.ID","trtrue",E2dt1,between = "condition",within="sequence")
m

emdiff2<-emmeans(m,"condition")
emdiff2

con4<-list(true_vs_fake=c(1,-1))
contrast(emdiff2, con4, adjust = "holm")

#reset e2dt1 to subset
E2dt1<-E2dur[,(1:7)]
E2dt1<-E2dt1[,-(5:6)]

#t.tests
E2dt1mf<-E2dt1%>%filter(condition=="More Fake")
t.test(E2dt1mf$trlast8,E2dt1mf$trfirst8,paired = TRUE)
colnames(E2dt1mf)

E2dt1at<-E2dt1%>%filter(condition=="All True")
t.test(E2dt1at$trlast8,E2dt1at$trfirst8,paired = TRUE) ##significant 

#difference
E2dt1<-E2dt1%>%mutate(difference=trlast8-trfirst8)
mdiff<-aov_ez("Respond.ID","difference",E2dt1,between = "condition")
mdiff

afex_plot(mdiff,"condition",error = "between",mapping = "color")

tr_s2_diff<-emmeans(mdiff,"condition")
tr_s2_diff

tr_s2_diff%>%
  pairs(adjust="holm")

anova_model_e2trdiff = lm(formula = difference ~ condition, data = E2dt1)
summary.aov(anova_model_e2trdiff)

eta.full.SS(dfm = 1, dfe = 77, ssm = 0.2002,
            sst = (0.2002+2.0263), Fvalue = 7.609, a = .05)


emdiff<-emmeans(mdiff,"condition")
emdiff

con5<-list(true_vs_fake=c(1,-1))
contrast(emdiff, con5, adjust = "holm")

with(E2dt1, hist(trfirst8))
with(E2dt1, hist(trlast8))
with(E2dt1,hist(difference))

m7<-filter(E2dt1,condition=="More Fake")
m8<-filter(E2dt1,condition=="All True")

#Figure 2
p_s2 <- ggplot(E2dt1, aes(x=condition, y=difference)) + 
  labs(y="Change of Truth Relativism ", x = "Treatment Group") +
  geom_boxplot(alpha=0.3,width = .15,outlier.shape = NA,fill="dark grey")+
  theme_classic()+
  geom_point(position = position_jitter(width = .15), size = 0.5,colour="black")
p_s2
p_s2<-p_s2+theme_apa() ##where to add theme_apa
p_s2
```

## Research question 2: examine whether differential exposure to misinformation affects individuals’ accuracy of judgements 
```{r}
#Analysis of accuracy
E2dt<-read.csv("E2dt.csv",header=TRUE)
E2dt_derandomize<- read.csv("E2dt_derandomize.csv",header = TRUE) 

#reread
responseArray2<- read.csv("responseArray2.csv",header = TRUE)

for(i in 1:nrow(responseArray2)){
  for(j in 1:length(responseArray2)){
    if(is.na(responseArray2[i,j])==TRUE){
      responseArray2[i,j]<-responseArray2$s_mean[i]
      }
        }
}

responseArray2<-responseArray2[,-81]
responseArray2[,81:85]<-E2dt[,4:8]

responseArray2$Duration..in.seconds.<-E2dt$Duration..in.seconds. #86
responseArray2$Response.ID<-E2dt$Response.ID #87
responseArray2$condition<-E2dt$condition #88
responseArray2[,89:107]<-E2dt[,89:107]

#put respond.id...in the start 
responseArray2<-responseArray2[,c(86,87,88,81,82,83,84,85,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73,74,75,76,77,78,79,80,89,90,91,92,93,94,95,96,97,98,99,100,101,102,103,104,105,106,107)]

E2dt2<-responseArray2
E2dt2[E2dt2$condition=="All True ","condition"] <- "All True"
E2dt2[E2dt2$condition=="More Fake ","condition"] <- "More Fake"

E2dt2 <- subset(E2dt2, E2dt2$Duration..in.seconds. < 10000)
hist(E2dt2$Duration..in.seconds., 50)

for(i in 1:nrow(E2dt2)){
   for(j in c(9,10,11,12,13,14,15,16,81,82,83,84,85,86,87,88)){
     if(E2dt2[i,j]<50)
     {E2dt2[i,j]<-0 }
     else if (E2dt2[i,j]==50)
     {E2dt2[i,j]<-0.5}
     else{
       E2dt2[i,j]<-1
     }
         }
}

E2dt21<-E2dt2%>%filter(condition=="More Fake")
for(i in 1:nrow(E2dt21)){
   for(j in c(17:80)){
     if(E2dt21[i,j]<50 )
     {E2dt21[i,j]<-1}
     else if (E2dt21[i,j]==50)
     {E2dt21[i,j]<-0.5}
     else{
       E2dt21[i,j]<-0
     }
         }
 }

E2dt22<-E2dt2%>%filter(condition=="All True")
for(i in 1:nrow(E2dt22)){
   for(j in c(17:80)){
     if(E2dt22[i,j]<50 )
     {E2dt22[i,j]<-0}
     else if (E2dt22[i,j]==50)
     {E2dt22[i,j]<-0.5}
     else{
       E2dt22[i,j]<-1
     }
         }
}

E2dt2_bind<-rbind(E2dt21,E2dt22)
E2dt2_bind_16<-E2dt2_bind[,-c(17:80)] #only remain first 8 and last 8 

E2dt2_bind<-E2dt2_bind %>%
  dplyr::group_by(Response.ID) %>%
    summarize(percentage = sum(c(X,X.1,          X.2 ,         X.3,          X.4,         
X.5 ,    X.6,     X.7 ,        X.8 ,         X.9 ,         X.10 ,    X.11,    
X.12 ,        X.13,         X.14,         X.15 ,   X.16,        X.17  ,       X.18  ,      
X.19  ,   X.20,   X.21 ,        X.22 ,        X.23 ,        X.24,X.25,X.26,X.27,X.28,X.29,X.30,X.31,X.32,X.33,X.34,X.35,X.36,X.37,X.38,X.39,X.40,X.41,X.42,X.43,X.44,X.45,X.46,X.47,X.48,X.49,X.50,X.51,X.52,X.53,X.54,X.55,X.56,X.57,X.58,X.59,X.60,X.61,X.62,X.63,X.64,X.65,X.66,X.67,X.68,X.69,X.70,X.71,X.72,X.73,X.74,X.75,X.76,X.77,X.78,X.79)/80*100))  %>%
inner_join(E2dt2_bind, by = 'Response.ID')

E2dt2_bind<-E2dt2_bind %>%
  group_by(Response.ID) %>%
    summarize(disMiddle = sum(c(X.8,X.9 ,         X.10 ,    X.11,    
X.12 ,        X.13,         X.14,         X.15 ,   X.16,        X.17  ,       X.18  ,      
X.19  ,   X.20,   X.21 ,        X.22 ,        X.23 ,        X.24,X.25,X.26,X.27,X.28,X.29,X.30,X.31,X.32,X.33,X.34,X.35,X.36,X.37,X.38,X.39,X.40,X.41,X.42,X.43,X.44,X.45,X.46,X.47,X.48,X.49,X.50,X.51,X.52,X.53,X.54,X.55,X.56,X.57,X.58,X.59,X.60,X.61,X.62,X.63,X.64,X.65,X.66,X.67,X.68,X.69,X.70,X.71)/64*100)) %>%
inner_join(E2dt2_bind, by = 'Response.ID')

E2dt2_bind_16<-E2dt2_bind_16 %>%
  group_by(Response.ID) %>%
    summarize(percentage_f8 = sum(c(X,X.1,X.2,X.3,X.4,X.5,X.6,X.7)/8*100)) %>%
inner_join(E2dt2_bind_16, by = 'Response.ID')

E2dt2_bind_16<-E2dt2_bind_16 %>%
  group_by(Response.ID) %>%
    summarize(percentage_l8 = sum(c(X.72,X.73,X.74,X.75,X.76,X.77,X.78,X.79)/8*100)) %>%
inner_join(E2dt2_bind_16, by = 'Response.ID')

E2dt2_bind_16<-E2dt2_bind_16%>%mutate(difference_accu=percentage_l8-percentage_f8)

#Anovas of accuracy
E2dur2 <- subset(E2dt2_bind, E2dt2_bind$Duration..in.seconds. < 10000)
E2dur2_16 <- subset(E2dt2_bind_16, E2dt2_bind_16$Duration..in.seconds. < 10000)

maccu<-aov_ez("Response.ID","percentage",E2dt2_bind,between = "condition")
maccu

maccu2<-aov_ez("Response.ID","percentage",E2dur2,between = "condition")
maccu2

afex_plot(maccu2,"condition",error = "between",mapping = "color")

tr_s2_accu80<-emmeans(maccu2,"condition")
tr_s2_accu80

tr_s2_accu80%>%
  pairs(adjust="holm")

m3<-filter(E2dur2,condition=="More Fake")
m4<-filter(E2dur2,condition=="All True")

m9<-filter(E2dur2_16,condition=="More Fake")
m10<-filter(E2dur2_16,condition=="All True")

maccu_f8<-aov_ez("Response.ID","percentage_f8",E2dt2_bind_16,between = "condition")
maccu_f8
maccu_f82<-aov_ez("Response.ID","percentage_f8",E2dur2_16,between = "condition")
maccu_f82

afex_plot(maccu_f82,"condition",error = "between",mapping = "color")

tr_s2_accu_f8<-emmeans(maccu_f82,"condition")
tr_s2_accu_f8

tr_s2_accu_f8%>%
  pairs(adjust="holm")

maccu_l8<-aov_ez("Response.ID","percentage_l8",E2dt2_bind_16,between = "condition")
maccu_l8
maccu_l82<-aov_ez("Response.ID","percentage_l8",E2dur2_16,between = "condition")
maccu_l82 

afex_plot(maccu_l82,"condition",error = "between",mapping = "color")

tr_s2_accu_l8<-emmeans(maccu_l82,"condition")
tr_s2_accu_l8

tr_s2_accu_l8%>%
  pairs(adjust="holm")

maccu_m64<-aov_ez("Response.ID","disMiddle",E2dt2_bind,between = "condition")
maccu_m64

afex_plot(maccu_m64,"condition",error = "between",mapping = "color")

tr_s2_accu_m64<-emmeans(maccu_m64,"condition")
tr_s2_accu_m64

tr_s2_accu_m64%>%
  pairs(adjust="holm")

eaccu<-emmeans(maccu,"condition")
eaccu

eaccu2<-emmeans(maccu2,"condition")
eaccu2

eaccu_l82<-emmeans(maccu_l82,"condition")
eaccu_l82

eaccu_l8<-emmeans(maccu_l8,"condition")
eaccu_l8

#Anova about difference in accuracy 
mdiff_accu<-aov_ez("Response.ID","difference_accu",E2dt2_bind_16,between = "condition")
mdiff_accu

mdiff_accu2<-aov_ez("Response.ID","difference_accu",E2dur2_16,,between ="condition")
mdiff_accu2

emdiff_accu<-emmeans(mdiff_accu,"condition")
emdiff_accu

anova_model_accudiff = lm(formula = difference_accu ~ condition, data = E2dur2_16)
summary.aov(anova_model_accudiff)

eta.full.SS(dfm = 1, dfe = 77, ssm = 77,
            sst = (77+41085), Fvalue = 0.145, a = .05)

#only remain f8/l8/id/conditions
E2dt2_bind_16_2<-E2dt2_bind_16[,c(1,2,3,5)]

#change trf8/trl8 into one column 
E2dt2_bind_16_2<-E2dt2_bind_16_2 %>%
  pivot_longer(c(2,3), names_to = "sequence", values_to = "percentagetrue")

#mixed anova \
mp<-aov_ez("Response.ID","percentagetrue",E2dt2_bind_16_2,between = "condition",within="sequence")
mp

emmp<-emmeans(mp,"condition")
emmp

#t test of differences in accuracy 
E2dt2_bind_16mf<-E2dt2_bind_16%>%filter(condition=="More Fake")
E2dt2_bind_16$condition
t.test(E2dt2_bind_16mf$percentage_l8,E2dt2_bind_16mf$percentage_f8,paired = TRUE)

E2dt2_bind_16at<-E2dt2_bind_16%>%filter(condition=="All True")
t.test(E2dt2_bind_16at$percentage_l8,E2dt2_bind_16at$percentage_f8,paired = TRUE)

```

##Other factors
```{r}
###other regressions 
#first merge e2dt,e2dt2bind and e2dt3bind so a chart has every information that we have 
E2<-cbind(E2dt1,E2dt2_bind)
E2<-E2[,-7]
E2<-E2[,-c(16:95)]
E2$tr80<-E2dur$tr80

#concern,frequency,sources
a<-lm(tr80~concern+frequency+sources,E2)
summary(a)

#exhaustion
ex<-aov_ez("Respond.ID","exhaustion",E2,between = "condition")
ex

afex_plot(ex,"condition",error = "between",mapping = "color")

tr_s2_ex<-emmeans(ex,"condition")
tr_s2_ex

tr_s2_ex%>%
  pairs(adjust="holm")

#partisanship
E2dt$partisanship.<-as.factor(E2dt$partisanship.)
levels(E2dt$partisanship.)

par<-aov_ez("Respond.ID","tr80",E2,between = "partisanship.")
par

group_by(E2, partisanship.) %>%
  summarise(
    count = n(),
    mean = mean(tr80),
    sd = sd(tr80)
  )

res.aov <- aov(tr80 ~ partisanship., data = E2)
summary(res.aov)

```


## Research question 3: examine the correlation between truth relativism and individual’s self-reported relativism
```{r}
#self report relativism 
E2<-E2 %>%
  group_by(Respond.ID) %>%
    summarize(sr = mean(c(s1,s2,s3,s4,s5,s6,s7,s8,s9,s10,s11))) %>%
inner_join(E2, by = 'Respond.ID')

E2<-read.csv("E2.csv",header = TRUE)

anova_model_e2sr = lm(formula = sr ~ tr80, data = E2)
summary.aov(anova_model_e2sr)

eta.full.SS(dfm = 1, dfe = 77, ssm = 1.595,
            sst = (1.595+18.945), Fvalue = 6.482, a = .05)

se<-aov_ez("Respond.ID","sr",E2,between = "condition")
se

enfse<-emmeans(se,"condition")
enfse

afex_plot(se,"condition",error = "between",mapping = "color")

tr_s2_se<-emmeans(se,"condition")
tr_s2_se

tr_s2_se%>%
  pairs(adjust="holm")

#concern,frequency and sources with self-report relativism 
asr<-lm(sr~concern+frequency+sources,E2)
summary(asr)

bsr<-lm(sr~concern+sources,E2)
summary(bsr)

csr<-lm(sr~sources,E2)
summary(csr)

dsr<-lm(sr~concern,E2)
summary(dsr)

esr<-lm(sr~concern+frequency,E2)
summary(esr)

fsr<-lm(sr~sources+frequency,E2)
summary(fsr)

gsr<-lm(sr~frequency,E2)
summary(gsr)

summary(lm(sources~frequency,E2))
summary(lm(sources~concern,E2))

#partisanship and self-report relativism 
E2dt$partisanshi.<-as.factor(E2dt$partisanship.)

par_sr<-aov_ez("Respond.ID","sr",E2,between = "partisanship.")
par_sr

res.aovsr <- aov(sr ~ partisanship., data = E2)
summary(res.aovsr)
```

##Analysis of "encounter", "fake news experience" and the number of sliders participants put less than 50
##“Among all the news you have just read in our experiment, what percentage of fake news do you think you have encountered?” - "encounter"
##We asked the question: “In your opinion, what is the percentage of fake news among all the news that you encounter?” - "fake news experience"
```{r}
#manipulation check -encounter
man<-aov_ez("Respond.ID","encounter",E2,between = "condition")
man

emencounter<-emmeans(man,"condition")
emencounter
con6<-list(true_vs_fake=c(1,-1))
contrast(emencounter, con6, adjust = "holm")

#subjective fake news experience 
summary(lm(tr80~subjective,E2)) 

summary(lm(tr80~encounter,E2)) 

summary(lm(tr80~sr,E2)) 
cor.test(E2$tr80,E2$sr)

summary(lm(sr~subjective,E2))
summary(lm(sr~encounter,E2))
summary(lm(encounter~subjective,E2)) 

summary(lm(percentage~subjective,E2))
summary(lm(percentage~encounter,E2))

#number of fake news judgements 
E2dtjudgement<-E2dt2

for(i in 1:nrow(E2dtjudgement)){
   for(j in c(9:88)){
     if(E2dtjudgement[i,j]<50 )
     {E2dtjudgement[i,j]<-1}
     else if (E2dtjudgement[i,j]==50 ){
       E2dtjudgement[i,j]<-0.5
     }
     else{
       E2dtjudgement[i,j]<-0
     }
         }
}


E2dtjudgement<-E2dtjudgement %>%
  group_by(Response.ID) %>%
    summarize(judgement =sum (c(X,X.1,          X.2 ,         X.3,          X.4,         
X.5 ,    X.6,     X.7 ,        X.8 ,         X.9 ,         X.10 ,    X.11,    
X.12 ,        X.13,         X.14,         X.15 ,   X.16,        X.17  ,       X.18  ,      
X.19  ,   X.20,   X.21 ,        X.22 ,        X.23 ,        X.24,X.25,X.26,X.27,X.28,X.29,X.30,X.31,X.32,X.33,X.34,X.35,X.36,X.37,X.38,X.39,X.40,X.41,X.42,X.43,X.44,X.45,X.46,X.47,X.48,X.49,X.50,X.51,X.52,X.53,X.54,X.55,X.56,X.57,X.58,X.59,X.60,X.61,X.62,X.63,X.64,X.65,X.66,X.67,X.68,X.69,X.70,X.71,X.72,X.73,X.74,X.75,X.76,X.77,X.78,X.79))) %>%
inner_join(E2dtjudgement, by = 'Response.ID')

E2$judgement<-E2dtjudgement$judgement

#regressions regarding fake news judgements 
summary(lm(encounter~judgement,E2)) #effective question about encounter 
summary(lm(sr~judgement,E2)) 
summary(lm(tr80~judgement,E2)) 

E2$difference
summary(lm(tr80~judgement,E2)) 
summary(lm(tr80~judgement,E2)) 

```

##Regressions
```{r}
#regressions regarding accuracy
summary(lm(percentage~tr80,E2))  #negative relationship between accuracy and relativism

summary(lm(percentage~sr,E2)) 

summary(lm(tr80~sr,E2))

summary(lm(percentage~concern+frequency+sources,E2))
#negative relationship between detailed accuracy and relativism

#regressions regarding exhaustion 
summary(lm(tr80~exhaustion,E2))

summary(lm(percentage~exhaustion,E2)) #the more exhausted, the less discerned 

summary(lm(exhaustion~subjective,E2)) #the more exhausted, the 
cor.test(E2$exhaustion,E2$subjective)

summary(lm(encounter~exhaustion,E2))  #the more exhausted, the more encounter

summary(lm(judgement~exhaustion,E2))

summary(lm(judgement~exhaustion,E2))

summary(lm(judgement~subjective,E2))

cor.test(E2$judgement,E2$subjective)

summary(lm(encounter~subjective,E2))

summary(lm(subjective~encounter,E2))

summary(lm(tr80~subjective,E2))

summary(lm(trlast8~subjective,E2))

summary(lm(trfirst8~subjective,E2))

summary(lm(difference~subjective,E2))

colnames(E2)

#other regressions 
summary(lm(tr80~sr,E2))
summary(lm(tr80~age,E2))
summary(lm(difference~age,E2)) 


summary(lm(trlast8~age,E2))
summary(lm(trfirst8~age,E2))

summary(lm(sr~age,E2))

summary(lm(tr80~sr+condition,E2))
summary(lm(tr80~judgement+condition,E2))

summary(lm(tr80~gender,E2))
summary(lm(sr~gender,E2)) 

aov_ez("Respond.ID","tr80",E2,between = "gender")
aov_ez("Respond.ID","sr",E2,between = "gender")

#gender and self-report relativism
summary(lm(percentage~judgement ,E2)) 
E2$percentage_f8<-E2dt2_bind_16$percentage_f8
E2$percentage_l8<-E2dt2_bind_16$percentage_l8
E2$percentage_disMiddle<-E2dt2_bind$disMiddle
E2$difference_accu<-E2dt2_bind_16$difference_accu

summary(lm(percentage~judgement ,E2)) 

summary(lm(percentage_f8~judgement ,E2)) 
summary(lm(percentage_l8~judgement ,E2)) 

summary(lm(difference_accu~judgement ,E2)) 

aov_ez("Respond.ID","tr80",E2,between = "age")

median(E2$percentage)

median(E2$percentage)
median(E2$percentage_l8)
median(E2$percentage_f8)
```

