---
title: "Study 1"
output: html_document
---

```{r}
library("Rmisc")
library("plyr")
library("lattice")
library("ggplot2")
library("ggpubr")
library("plotrix")
library("rtdists")
library("tidyverse")
library("tidyr")
library("afex")
library("emmeans")
library("viridis")
library("cowplot")
library("stringr")
library("caret")
library("cowplot")
library("knitr")
library("lattice")
library("gsubfn") 
library("stringi")    
library("nlme")
library("Matrix")
library("writexl")
library("xlsx")
library("PairedData")
library(yarrr)     
library(plotrix)   
library(kableExtra)
library(jtools)
library(here)   
here::here()
library(psycho)
library("dplyr")
library("data.table")
library("lsr")
library(MOTE)
library(pwr)

#theme_apa
theme_apa <- function(base_size = 12, base_family = "", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(
      plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0), hjust = 0.5)
      , plot.subtitle = ggplot2::element_text(size = ggplot2::rel(0.8), margin = ggplot2::margin(ggplot2::rel(-7), 0, ggplot2::rel(14), 0), hjust = 0.5)

      # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
      , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
      , axis.title.x.top = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(12), 0))
      , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
      , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
      , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
      , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
      , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
      , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
      , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
      , axis.line = ggplot2::element_line()
      # , axis.line.x = ggplot2::element_line()
      # , axis.line.y = ggplot2::element_line()

      , legend.title = ggplot2::element_text()
      , legend.key = ggplot2::element_rect(fill = NA, color = NA)
      , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.margin = ggplot2::margin(
        t = ggplot2::rel(16)
        , r = ggplot2::rel(16)
        , b = ggplot2::rel(16)
        , l = ggplot2::rel(16)
        , unit = "points"
      )

      , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
      , panel.grid.major.x = ggplot2::element_blank()
      , panel.grid.minor.x = ggplot2::element_blank()
      , panel.grid.major.y = ggplot2::element_blank()
      , panel.grid.minor.y = ggplot2::element_blank()

      , strip.background = ggplot2::element_rect(fill = NA, color = NA)
      , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
      , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )

  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }

  adapted_theme
}
```

## Research question 1: investigate if and how differential exposure to misinformation affects individuals’ truth relativism towards true news
```{r cars}
#Reading data
dt200<-read.csv("tn200.csv",header=TRUE)

#Data transformation - from true level to truth relativism 
for(i in 1:nrow(dt200)) {
  for (j in 4:43){
    dt200[i,j]<-(1-abs(dt200[i,j]-50)/50)
  }
}

#Treatment groups
dt1_headlinelessfake<-data.frame(colMeans(filter(dt200,condition=="Less Fake")[,4:43]))
dt1_headlinemorefake<-data.frame(colMeans(filter(dt200,condition=="More Fake")[,4:43]))

#Truth relativism of 20 common headlines
dt200<-dt200 %>%
  group_by(participant) %>%
    summarize(tr20 = mean(c(X1,          X2 ,         X3,          X4,         
X5 ,         X7 ,        X8 ,         X9 ,         X10 ,        
X12 ,        X13,         X14,         X15 ,           X17  ,       X18  ,      
X19  ,      X21 ,        X22 ,        X23 ,        X24 ))) %>%
inner_join(dt200, by = 'participant')

#Truth relativism of all the headlines 
dt200<-dt200 %>%
  group_by(participant) %>%
    summarize(trall = mean(c(X1,          X2 ,         X3,          X4,         
X5 ,  X6,    X7 ,        X8 ,         X9 ,         X10 ,      X11,  
X12 ,        X13,         X14,         X15 ,    X16,       X17  ,       X18  ,      
X19  ,   X20,   X21 ,        X22 ,        X23 ,        X24,X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X36,X37,X38,X39,X40))) %>%
inner_join(dt200, by = 'participant')

#Anova of truth relativism of 20 common headlines 
nf200<-aov_ez("participant","tr20",dt200,between = c("feedback","condition"))
nf200

anova_modele1tr = lm(formula = tr20 ~ condition, data = dt200)
summary.aov(anova_modele1tr)

eta.full.SS(dfm = 1, dfe = 180, ssm = 0.003,
            sst = (0.003+5.878), Fvalue = 0.081, a = .05)

#afex_plot
afex_plot(nf200,"feedback","condition",error = "between",mapping = c("shape", "color"))

#Follow-up
enf200<-emmeans(nf200,"condition",by="feedback")

enf2001<-emmeans(nf200,"feedback",by="condition")
enf2001

enf200%>%
  pairs(adjust="holm")

enf2001%>%
  pairs(adjust="holm") 

#Main graph for Study 1
dt200 %>%
  arrange("Truth Relativism") %>%
  mutate(X = factor(X, levels=c("Less Fake & No Feedback", "More Fake & No Feedback","Less Fake & With Feedback", "More Fake & With Feedback"))) %>%
 ggplot(aes(x=X, y=tr20)) + 
  labs(y="Truth Relativism", x = "Treatment Group") +
  geom_boxplot(alpha=0.3,width = .15,outlier.shape = NA,fill="dark grey")+
  theme_classic()+
  geom_point(position = position_jitter(width = .15), size = 0.5,colour="black")
```

## Analysis of the percentage of news that were rated less than 50
```{r pressure, echo=FALSE}
#Analysis of the percentage of news that were rated less than 50
dt200dis<-read.csv("tn200.csv",head=TRUE)

#Data transformation
for(i in 1:nrow(dt200dis)){
   for(j in 4:43){
     if(dt200dis[i,j]<50)
     {dt200dis[i,j]<-1}
     else if (dt200dis[i,j]==50)
     {dt200dis[i,j]<-0.5}
     else{
       dt200dis[i,j]<-0
     }
         }
 }

#the_percentage_of_news_that_were_rated_less_than50
dt200dis<-dt200dis %>%
  group_by(participant) %>%
    summarize(the_percentage_of_news_that_were_rated_less_than50 = sum(c(X1,          X2 ,         X3,          X4,         
X5 ,   X6,      X7 ,        X8 ,         X9 ,         X10 ,        X11,
X12 ,        X13,         X14,         X15 ,    X16,       X17  ,       X18  ,      
X19  ,  X20,    X21 ,        X22 ,        X23 ,        X24,X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X36,X37,X38,X39,X40)/40*100)) %>%
inner_join(dt200dis, by = 'participant')

#Manipulation check 
dt200dis%>%
  group_by(feedback,condition)%>%
  summarise(mean=mean(the_percentage_of_news_that_were_rated_less_than50),
            sd=sd(the_percentage_of_news_that_were_rated_less_than50))

#Anova of the percentage of news that were rated less than 50
fakepercentage<-aov_ez("participant","the_percentage_of_news_that_were_rated_less_than50",dt200dis,between = c("feedback","condition"))
summary(fakepercentage)

#Afex_plot
afex_plot(fakepercentage,"feedback","condition",error = "between",mapping = c("shape", "color"))

#Follow-up for the percentage of news that were rated less than 50
percentage1<-emmeans(fakepercentage,"condition","feedback")
percentage1

percentage2<-emmeans(fakepercentage,"feedback",by="condition")
percentage2

percentage3<-emmeans(fakepercentage,"condition")
percentage3

percentage4<-emmeans(fakepercentage,"feedback")
percentage4

con1<-list(mixed_vs_true=c(1,-1))
contrast(percentage3, con1, adjust = "holm")

con3<-list(yf_vs_nf=c(-1,1))
contrast(percentage4, con3, adjust = "holm")

percentage1%>%
  pairs(adjust="holm")

percentage2%>%
  pairs(adjust="holm")

```


## Research question 2: examine whether differential exposure to misinformation affects individuals’ accuracy of judgements 
```{r}
#Analysis of accuracy
dt200right<-read.csv("tn200.csv",head=TRUE)

dt200true<-dt200right%>%
  filter(condition=="Less Fake")

for(i in 1:nrow(dt200true)) {
  for (j in c(4,5,6,7,8,10,11,12,13,15,16,17,18,20,21,22,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,40,41,42,43)){
    if (dt200true[i,j]<50)
    {dt200true[i,j]<-0}
     else if (dt200true[i,j]==50)
     {dt200true[i,j]<-0.5}
    else
      {dt200true[i,j]<-1}
  }
}

for(i in 1:nrow(dt200true)) {
  for (j in c(9,14,19,23,39)){
    if (dt200true[i,j]<50)
    {dt200true[i,j]<-1}
    else if (dt200true[i,j]==50)
     {dt200true[i,j]<-0.5}
    else
      {dt200true[i,j]<-0}
  }
}

dt200true<-dt200true %>%
  group_by(participant) %>%
    summarize(discernment40true = sum(c(X1,          X2 ,         X3,          X4,  
X5 ,  X7 ,        X8 ,         X9 ,         X10 ,  
X12 ,        X13,         X14,         X15 ,      X17  ,       X18  ,      
X19  ,   X21 ,        X22 ,        X23 ,        X24,X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X37,X38,X39,X40)/35*100)) %>%
inner_join(dt200true, by = 'participant')

dt200true<-dt200true %>%
  group_by(participant) %>%
    summarize(discernment40false= sum(c(X6,X11,X16,X20,X36)/5*100)) %>%
inner_join(dt200true, by = 'participant')

dt200true<-dt200true %>%
  group_by(participant) %>%
    summarize(discernment40falsecommon= sum(c(X6,X11,X16,X20,X36)/5*100)) %>%
inner_join(dt200true, by = 'participant')

dt200true<-dt200true %>%
  group_by(participant) %>%
    summarize(discernment40truecommon = sum(c(X1,          X2 ,         X3,          X4,  
X5 ,  X7 ,        X8 ,         X9 ,         X10 ,  
X12 ,        X13,         X14,         X15 ,      X17  ,       X18  ,      
X19  ,   X21 ,        X22 ,        X23 ,        X24)/20*100)) %>%
inner_join(dt200true, by = 'participant')

dt200true<-dt200true %>%
  group_by(participant) %>%
    summarize(discernment40= sum(c(X1,          X2 ,         X3,          X4,  
X5 ,  X6,       X7 ,        X8 ,         X9 ,         X10 ,     X11,   
X12 ,        X13,         X14,         X15 ,   X16,        X17  ,       X18  ,      
X19  ,   X20,   X21 ,        X22 ,        X23 ,        X24,X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X36,X37,X38,X39,X40)/40*100)) %>%
inner_join(dt200true, by = 'participant')

dt200true<-dt200true %>%
  group_by(participant) %>%
    summarize(discernment_other15 = sum(c(X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X37,X38,X39,X40)/15*100)) %>%
inner_join(dt200true, by = 'participant')

dt200mixed<-dt200right%>%
  filter(condition=="More Fake")

for(i in 1:nrow(dt200mixed)) {
  for (j in c(4,5,6,7,8,10,11,12,13,15,16,17,18,20,21,22,24,25,26,27)){
    if (dt200mixed[i,j]<50)
    {dt200mixed[i,j]<-0}
  else if (dt200mixed[i,j]==50)
     {dt200mixed[i,j]<-0.5}
    else
      {dt200mixed[i,j]<-1}
  }
}

for(i in 1:nrow(dt200mixed)) {
  for (j in c(9,14,19,23,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43)){
    if (dt200mixed[i,j]<50)
    {dt200mixed[i,j]<-1}
    else if (dt200mixed[i,j]==50)
     {dt200mixed[i,j]<-0.5}
    else
      {dt200mixed[i,j]<-0}
  }
}

dt200mixed<-dt200mixed %>%
  group_by(participant) %>%
    summarize(discernment40true = sum(c(X1,          X2 ,         X3,          X4,  
X5 ,  X7 ,        X8 ,         X9 ,         X10 ,  
X12 ,        X13,         X14,         X15 ,      X17  ,       X18  ,      
X19  ,   X21 ,        X22 ,        X23 ,        X24)/20*100)) %>%
inner_join(dt200mixed, by = 'participant')

dt200mixed<-dt200mixed %>%
  group_by(participant) %>%
    summarize(discernment40truecommon = sum(c(X1,          X2 ,         X3,          X4,  
X5 ,  X7 ,        X8 ,         X9 ,         X10 ,  
X12 ,        X13,         X14,         X15 ,      X17  ,       X18  ,      
X19  ,   X21 ,        X22 ,        X23 ,        X24)/20*100)) %>%
inner_join(dt200mixed, by = 'participant')

dt200mixed<-dt200mixed %>%
  group_by(participant) %>%
    summarize(discernment40false = sum(c(X6,X11,X16,X20,X36,X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X37,X38,X39,X40)/20*100)) %>%
inner_join(dt200mixed, by = 'participant')

dt200mixed<-dt200mixed%>%
  group_by(participant) %>%
    summarize(discernment40falsecommon= sum(c(X6,X11,X16,X20,X36)/5*100)) %>%
inner_join(dt200mixed, by = 'participant')

dt200mixed<-dt200mixed %>%
  group_by(participant) %>%
    summarize(discernment40 = sum(c(X1,          X2 ,         X3,          X4,         
X5 ,  X6,       X7 ,        X8 ,         X9 ,         X10 ,     X11,   
X12 ,        X13,         X14,         X15 ,   X16,        X17  ,       X18  ,      
X19  ,   X20,   X21 ,        X22 ,        X23 ,        X24,X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X36,X37,X38,X39,X40)/40*100)) %>%
inner_join(dt200mixed, by = 'participant')

dt200mixed<-dt200mixed %>%
  group_by(participant) %>%
    summarize(discernment_other15 = sum(c(X25,X26,X27,X28,X29,X30,X31,X32,X33,X34,X35,X37,X38,X39,X40)/15*100)) %>%
inner_join(dt200mixed, by = 'participant')

#Comparisons of accuracy between treatment groups 
dt200ability<-rbind(dt200true,dt200mixed)

dt200$discernment40truecommon<-dt200ability$discernment40truecommon

dt200ability%>%
  group_by(feedback,condition)%>%
  summarise(mean=mean(discernment40),
            sd=sd(discernment40)) 

dt200ability%>%
  group_by(feedback,condition)%>%
  summarise(mean=mean(discernment40truecommon),
            sd=sd(discernment40truecommon)) 

dt200ability%>%
  group_by(feedback,condition)%>%
  summarise(mean=mean(discernment40falsecommon),
            sd=sd(discernment40falsecommon)) 

dt200ability%>%
  group_by(feedback,condition)%>%
  summarise(mean=mean(discernment_other15),
            sd=sd(discernment_other15)) 

#Anovas of accuracy between treatment groups 
discernment40<-aov_ez("participant","discernment40",dt200ability,between = c("feedback","condition"))
summary(discernment40)

discernment40truecommon<-aov_ez("participant","discernment40truecommon",dt200ability,between = c("feedback","condition"))
summary(discernment40truecommon)

discernment40falsecommon<-aov_ez("participant","discernment40falsecommon",dt200ability,between = c("feedback","condition"))
summary(discernment40falsecommon)

afex_plot(discernment40,"feedback","condition",error = "between",mapping = c("shape", "color"))

discernment1<-emmeans(discernment40,"condition","feedback")
discernment1

discernment2<-emmeans(discernment40,"feedback",by="condition")
discernment2

discernment3<-emmeans(discernment40,"condition")
discernment3

discernment4<-emmeans(discernment40,"feedback")
discernment4

con4<-list(mixed_vs_true=c(1,-1))
contrast(discernment3, con4, adjust = "holm")

con5<-list(yf_vs_nf=c(-1,1))
contrast(discernment4, con5, adjust = "holm")

con6<-list(yf_vs_nf=c(-0.5,-0.5,0.5,0.5),
           mixed_vs_true=c(0.5,-0.5,0.5,-0.5))

discernment1%>%
  pairs(adjust="holm")

discernment2%>%
  pairs(adjust="holm")

discernment_other<-aov_ez("participant","discernment_other15",dt200ability,between = c("feedback","condition"))
summary(discernment_other)

afex_plot(discernment_other,"feedback","condition",error = "between",mapping = c("shape", "color"))

discernment1_other<-emmeans(discernment_other,"condition","feedback")
discernment1_other

discernment2_other<-emmeans(discernment_other,"feedback",by="condition")
discernment2_other

discernment1_other%>%
  pairs(adjust="holm")

discernment2_other%>%
  pairs(adjust="holm")
```


#Analysis of other factors
```{r}
#concern,frequency,sources
a<-lm(trall~concern+frequency+sources,dt200)
summary(a)
a20<-lm(tr20~concern+frequency+sources,dt200)
summary(a20)

#Analysis of exhaustion
ex<-aov_ez("participant","exhaustion",dt200,between = c("feedback","condition"))
ex

exfo<-emmeans(ex,"condition",by="feedback")
exfo

exfo1<-emmeans(ex,"feedback",by="condition")
exfo1

exfo%>%
  pairs(adjust="holm")

exfo1%>%
  pairs(adjust="holm")

#Analysis of partisanship
dt200$partisanship<-as.factor(dt200$partisanship)
levels(dt200$partisanship)

par<-aov_ez("participant","tr20",dt200,between = "partisanship")
par

group_by(dt200, partisanship) %>%
  summarise(
    count = n(),
    mean = mean(trall),
    sd = sd(trall)
  )


group_by(dt200, partisanship) %>%
  summarise(
    count = n(),
    mean = mean(tr20),
    sd = sd(tr20)
  )

#Analysis of Cognitive Reflection Test score
for(i in 1:nrow(dt200)){
    if(dt200$crt1[i]==2) {
      dt200$crt1[i]<-1
      }
    else {
      dt200$crt1[i]<-0
    }
        }

for(i in 1:nrow(dt200)){
    if(dt200$crt2[i] %in% c("Emily","emily")) {
      dt200$crt2[i]<-1
      }
    else {
      dt200$crt2[i]<-0
    }
        }

for(i in 1:nrow(dt200)){
    if(dt200$crt3[i]==4) {
      dt200$crt3[i]<-1
      }
    else {
      dt200$crt3[i]<-0
    }
        }

for(i in 1:nrow(dt200)){
    if(dt200$crt4[i]==10) {
      dt200$crt4[i]<-1
      }
    else {
      dt200$crt4[i]<-0
    }
        }

for(i in 1:nrow(dt200)){
    if(dt200$crt4[i]==10) {
      dt200$crt4[i]<-1
      }
    else {
      dt200$crt4[i]<-0
    }
        }

for(i in 1:nrow(dt200)){
    if(dt200$crt5[i]==39) {
      dt200$crt5[i]<-1
      }
    else {
      dt200$crt5[i]<-0
    }
        }

for(i in 1:nrow(dt200)){
    if(dt200$crt6[i]==8) {
      dt200$crt6[i]<-1
      }
    else {
      dt200$crt6[i]<-0
    }
}

dt200$crt1<-as.numeric(dt200$crt1)
dt200$crt2<-as.numeric(dt200$crt2)
dt200$crt3<-as.numeric(dt200$crt3)
dt200$crt4<-as.numeric(dt200$crt4)
dt200$crt5<-as.numeric(dt200$crt5)
dt200$crt6<-as.numeric(dt200$crt6)

dt200<-dt200 %>%
  group_by(participant) %>%
    summarize(crt = sum(crt1,crt2,crt3,crt4,crt5,crt6))%>%
inner_join(dt200, by = 'participant')

res_crt<-lm(trall~crt,dt200)
summary(res_crt)

res_crt<-lm(tr20~crt,dt200)
summary(res_crt)
```

#Analysis of self-reported relativism
```{r}
se<-aov_ez("participant","sr",dt200,between = c("feedback","condition"))
se

anova_modele1sr = lm(formula = sr ~ tr20, data = dt200)
summary.aov(anova_modele1sr)

eta.full.SS(dfm = 1, dfe = 180, ssm = 634,
            sst = (634+10154), Fvalue = 11.25, a = .05)

enfse<-emmeans(se,"condition",by="feedback")
enfse

enfse%>%
  pairs(adjust="holm")

enfse1<-emmeans(se,"feedback",by="condition")
enfse1

enfse1%>%
  pairs(adjust="holm")

enfse2<-emmeans(se,"feedback")
enfse2

enfse2%>%
  pairs(adjust="holm")

cor.test(dt200$sr,dt200$tr20,method= "pearson")

cor.test(dt200$sr,dt200$trall)

asr<-lm(sr~concern+frequency+sources,dt200)
summary(asr)
#the more sources people check, the lower their self-report truth-relativism would be 

a<-lm(dt200ability$discernment40~concern+frequency+sources,dt200)
summary(a)

#partisanship and self-reported relativism 
dt200$partisanship<-as.factor(dt200$partisanship)

group_by(dt200, partisanship) %>%
  summarise(
    count = n(),
    mean = mean(sr),
    sd = sd(sr)
  )

res.aovsr <- aov(sr ~ partisanship, data = dt200)
summary(res.aovsr)

#crt and self-report relativism
res_crtsr<-lm(sr~crt,dt200)
summary(res_crtsr)

```


#Regressions of the percentage of news that were rated less than 50
```{r}
dt200$fp<-dt200dis$the_percentage_of_news_that_were_rated_less_than50

f3<-lm(exhaustion~fp,dt200)
summary(f3)

f4<-lm(sr~fp,dt200)
summary(f4)

summary(lm(fp~concern + frequency + sources,dt200))

summary(lm(fp~age,dt200))

summary(lm(tr20~age,dt200))

summary(lm(tr20~fp,dt200))

summary(aov_ez("participant","tr20",dt200,between = "condition"))

t.test(subset(dt200, condition=="Less Fake")$"tr20", 
       subset(dt200, condition=="More Fake")$"tr20")

summary(fakepercentage)

summary(lm(trall~age,dt200))
cor.test(dt200$sr,dt200$tr20)

dt200$discernment<-dt200ability$discernment40
dt200$discernment40truecommon<-dt200ability$discernment40truecommon
dt200$discernment40falsecommon<-dt200ability$discernment40falsecommon
dt200$discernment40false<-dt200ability$discernment40false
dt200$discernment40true<-dt200ability$discernment40true
dt200$discernment_other15<-dt200ability$discernment_other15
colnames(dt200ability)

d3<-lm(exhaustion~discernment,dt200)
summary(d3)

d4<-lm(sr~discernment,dt200)
summary(d4)

d5<-lm(discernment~crt,dt200)
summary(d5)

d6<-lm(crt~discernment,dt200)
summary(d6)

d7<-lm(discernment~concern + frequency + sources,dt200)
summary(d7)

d8<-lm(discernment~age,dt200)
summary(d8)

summary(lm(sr~age,dt200))
```

