---
title: "Study 3"
output: html_document
---

```{r setup, include=FALSE}
library("Rmisc")
library("plyr")
library("lattice")
library("ggplot2")
library("ggpubr")
#install.packages("plotrix")
library("plotrix")
#library("rgl")
library("rtdists")
library("tidyverse")
library("tidyr")
library("afex")
library("emmeans")
library("viridis")
library("cowplot")
library("stringr")
library("caret")
library("cowplot")
library("knitr")
library("lattice")
library("gsubfn") 
library("stringi")    
library("nlme")
library("Matrix")
library("writexl")
library("xlsx")
library("PairedData")
library(ggplot2) 
library(yarrr)     
library(tidyverse) 
library(plotrix)      
library(knitr)        
library(kableExtra) 
library(here)        
here::here()
library(psycho)
library("dplyr")
library("data.table")
library("MOTE")
library("pwr")
```

## Data formatting
```{r cars}
#original data
data_3<-read.csv("E3 original data downloaded from qualtrics.csv",header = TRUE)

#remove those who did not finish the experiment 
data_3<-subset(data_3,Progress==100)
#27 participants were excluded because they did not complete the experiment 100%, 90 participants remaining 

#remove survey preview
data_3<-subset(data_3,Status =='IP Address')
#2 previews were removed, 88 participants remaining 

#remove those who refused to take the experiment and chose the alternative task
data_3<-subset(data_3,Q3.4 =='I consent; proceed to the study.')
#1 participant was refused, 87 remaining 

#remove those that was me testing 
data_3<-subset(data_3,Warwick_Experimenter=='FALSE')
#2 were removed, 85 remaining

#remove data that we do not need 
#columns:
data_3<-data_3[,-c(1,2,3,4,5,7,8,10,11,12,13,14,15,16,17,18,27,36,69,78,122,124,125,126,127)]


#change characters into numeric
sapply(data_3, class)
cols.num <- c(5:85)
data_3[cols.num] <- sapply(data_3[cols.num],as.numeric)
sapply(data_3, class)

#means to replace nas 
data_3[24,c(7,8,9,10,11,12,13,14,15)]
data_3[24,6]<-mean(12,22,50,25,85,90,0,50,60)
data_3[24,6]


data_3[74,c(7,8,9,10,11,12,13,14,15)]
data_3[74,6]<-mean(59,67,75,52,68,47,33,56,63)
data_3[74,6]

data_3[79,c(7,8,9,10,11,12,13,14,15)]
data_3[79,6]<-mean(9,25,71,0,65,37,57,14,10)
data_3[79,6]

#add a column of condition
data_3$condition<-"all_true"

#distinguishing two conditions
for (i in 1:nrow(data_3)){
   if (is.na(data_3[i,46])==TRUE){
     data_3[i,103]<-"fake_include"
   }
}

#make subsets of two conditions 
data_3_fi<-subset(data_3,condition=="fake_include")
data_3_at<-subset(data_3,condition=="all_true")

#remove empty columns from each condition
data_3_at<-data_3_at[,-c(6:45)]
data_3_fi<-data_3_fi[,-c(46:85)]

#computation of accuracy for both data sets
sum(data_3_at[1,6:45]>50)

#all true condition: Targeted, NontargetedTrue1, TargetedTrue, NontargetedTrue2 
#accuracy for all the headlines
data_3_at$accu_all50ascorrect<-0
data_3_at$accu_all50aswrong<-0
data_3_at$accu_all50ashalf<-0
data_3_at$all_numberof50<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,64]<-(sum(data_3_at[i,6:15]>=50)+sum(data_3_at[i,16:25]>=50)+sum(data_3_at[i,26:35]>=50)+sum(data_3_at[i,36:45]>=50))/40
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,65]<-(sum(data_3_at[i,6:15]>50)+sum(data_3_at[i,16:25]>50)+sum(data_3_at[i,26:35]>50)+sum(data_3_at[i,36:45]>50))/40
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,66]<-(sum(data_3_at[i,6:15]>50)+sum(data_3_at[i,6:15]==50)/2+sum(data_3_at[i,16:25]>50)+sum(data_3_at[i,16:25]==50)/2+sum(data_3_at[i,26:35]>50)+sum(data_3_at[i,26:35]==50)/2+sum(data_3_at[i,36:45]>50)+sum(data_3_at[i,36:45]==50)/2)/40
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,67]<-(sum(data_3_at[i,6:15]==50)+sum(data_3_at[i,16:25]==50)+sum(data_3_at[i,26:35]==50)+sum(data_3_at[i,36:45]==50))
}

#accuracy for TargetedTrue
data_3_at$accu_Targeted_50ascorrect<-0
data_3_at$accu_Targeted_50aswrong<-0
data_3_at$accu_Targeted_50ashalf<-0
data_3_at$Targeted_numberof50<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,68]<-sum(data_3_at[i,6:15]>=50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,69]<-sum(data_3_at[i,6:15]>50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,70]<-(sum(data_3_at[i,6:15]>50)+sum(data_3_at[i,6:15]==50)/2)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,71]<-sum(data_3_at[i,6:15]==50)
}

#accuracy for NonTargetedTrue1
data_3_at$accu_NontargetedTrue1_50ascorrect<-0
data_3_at$accu_NontargetedTrue1_50aswrong<-0
data_3_at$accu_NontargetedTrue1_50ashalf<-0
data_3_at$NontargetedTrue1_numberof50<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,72]<-sum(data_3_at[i,16:25]>=50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,73]<-sum(data_3_at[i,16:25]>50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,74]<-(sum(data_3_at[i,16:25]>50)+sum(data_3_at[i,16:25]==50)/2)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,75]<-sum(data_3_at[i,16:25]==50)
}

#accuracy for TargetedTrue
data_3_at$accu_TargetedTrue_50ascorrect<-0
data_3_at$accu_TargetedTrue_50aswrong<-0
data_3_at$accu_TargetedTrue_50ashalf<-0
data_3_at$TargetedTrue_numberof50<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,76]<-sum(data_3_at[i,26:35]>=50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,77]<-sum(data_3_at[i,26:35]>50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,78]<-(sum(data_3_at[i,26:35]>50)+sum(data_3_at[i,26:35]==50)/2)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,79]<-sum(data_3_at[i,26:35]==50)
}

#accuracy for NontargetedTrue2
data_3_at$accu_NontargetedTrue2_50ascorrect<-0
data_3_at$accu_NontargetedTrue2_50aswrong<-0
data_3_at$accu_NontargetedTrue2_50ashalf<-0
data_3_at$NontargetedTrue2_numberof50<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,80]<-sum(data_3_at[i,36:45]>=50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,81]<-sum(data_3_at[i,36:45]>50)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,82]<-(sum(data_3_at[i,36:45]>50)+sum(data_3_at[i,36:45]==50)/2)/10
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,83]<-sum(data_3_at[i,36:45]==50)
}

#fake included condition: NontargetedTrue1, TargetedTrue, NontargetedTrue2, TargetedTrue
#accuracy for all the headlines
data_3_fi$accu_all50ascorrect<-0
data_3_fi$accu_all50aswrong<-0
data_3_fi$accu_all50ashalf<-0
data_3_fi$all_numberof50<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,64]<-(sum(data_3_fi[i,6:15]<=50)+sum(data_3_fi[i,16:25]>=50)+sum(data_3_fi[i,26:35]>=50)+sum(data_3_fi[i,36:45]>=50))/40
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,65]<-(sum(data_3_fi[i,6:15]<50)+sum(data_3_fi[i,16:25]>50)+sum(data_3_fi[i,26:35]>50)+sum(data_3_fi[i,36:45]>50))/40
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,66]<-(sum(data_3_fi[i,6:15]<50)+sum(data_3_fi[i,6:15]==50)/2+sum(data_3_fi[i,16:25]>50)+sum(data_3_fi[i,16:25]==50)/2+sum(data_3_fi[i,26:35]>50)+sum(data_3_fi[i,26:35]==50)/2+sum(data_3_fi[i,36:45]>50)+sum(data_3_fi[i,36:45]==50)/2)/40
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,67]<-(sum(data_3_fi[i,6:15]==50)+sum(data_3_fi[i,16:25]==50)+sum(data_3_fi[i,26:35]==50)+sum(data_3_fi[i,36:45]==50))
}

#accuracy for TargetedFake
data_3_fi$accu_Targeted_50ascorrect<-0
data_3_fi$accu_Targeted_50aswrong<-0
data_3_fi$accu_Targeted_50ashalf<-0
data_3_fi$Targeted_numberof50<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,68]<-sum(data_3_fi[i,6:15]<=50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,69]<-sum(data_3_fi[i,6:15]<50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,70]<-(sum(data_3_fi[i,6:15]<50)+sum(data_3_fi[i,6:15]==50)/2)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,71]<-sum(data_3_fi[i,6:15]==50)
}

#accuracy for NontargetedTrue1
data_3_fi$accu_NontargetedTrue1_50ascorrect<-0
data_3_fi$accu_NontargetedTrue1_50aswrong<-0
data_3_fi$accu_NontargetedTrue1_50ashalf<-0
data_3_fi$NontargetedTrue1_numberof50<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,72]<-sum(data_3_fi[i,16:25]>=50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,73]<-sum(data_3_fi[i,16:25]>50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,74]<-(sum(data_3_fi[i,16:25]>50)+sum(data_3_fi[i,16:25]==50)/2)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,75]<-sum(data_3_fi[i,16:25]==50)
}

#accuracy for TargetedTrue
data_3_fi$accu_TargetedTrue_50ascorrect<-0
data_3_fi$accu_TargetedTrue_50aswrong<-0
data_3_fi$accu_TargetedTrue_50ashalf<-0
data_3_fi$TargetedTrue_numberof50<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,76]<-sum(data_3_fi[i,26:35]>=50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,77]<-sum(data_3_fi[i,26:35]>50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,78]<-(sum(data_3_fi[i,26:35]>50)+sum(data_3_fi[i,26:35]==50)/2)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,79]<-sum(data_3_fi[i,26:35]==50)
}

#accuracy for NontargetedTrue2
data_3_fi$accu_NontargetedTrue2_50ascorrect<-0
data_3_fi$accu_NontargetedTrue2_50aswrong<-0
data_3_fi$accu_NontargetedTrue2_50ashalf<-0
data_3_fi$NontargetedTrue2_numberof50<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,80]<-sum(data_3_fi[i,36:45]>=50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,81]<-sum(data_3_fi[i,36:45]>50)/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,82]<-(sum(data_3_fi[i,36:45]>50)+sum(data_3_fi[i,36:45]==50))/10
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,83]<-sum(data_3_fi[i,36:45]==50)
}

#manipulation check 
data_3_at$all_sliderlessthan50<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,84]<-sum(data_3_at[i,6:45]<50)
}

data_3_fi$all_sliderlessthan50<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,84]<-sum(data_3_fi[i,6:45]<50)
}


#computation of truth relativism and new data set for it 
for(i in 1:nrow(data_3_at)) {
  for (j in 6:45){
    data_3_at[i,j]<-(1-abs(data_3_at[i,j]-50)/50)
  }
}

for(i in 1:nrow(data_3_fi)) {
  for (j in 6:45){
    data_3_fi[i,j]<-(1-abs(data_3_fi[i,j]-50)/50)
  }
}

#add a column of tr
#the mean value of truth relativism for all the news added as a new column for both data sets
rowMeans(data_3_at[,6:45])
data_3_at$tr_all<-rowMeans(data_3_at[,6:45])

rowMeans(data_3_fi[,6:45])
data_3_fi$tr_all<-rowMeans(data_3_fi[,6:45])

#the mean value of truth relativism for four subsets of news
#all true condition: NontargetedTrue1, TargetedFake, NontargetedTrue2, TargetedTrue
rowMeans(data_3_at[,6:15])
data_3_at$tr_Targeted<-rowMeans(data_3_at[,6:15])

rowMeans(data_3_at[,16:25])
data_3_at$tr_NontargetedTrue1<-rowMeans(data_3_at[,16:25])

rowMeans(data_3_at[,26:35])
data_3_at$tr_TargetedTrue<-rowMeans(data_3_at[,26:35])

rowMeans(data_3_at[,36:45])
data_3_at$tr_NontargetedTrue2<-rowMeans(data_3_at[,36:45])

#fake included condition: NontargetedTrue1, TargetedTrue, NontargetedTrue2, TargetedTrue
rowMeans(data_3_fi[,6:15])
data_3_fi$tr_Targeted<-rowMeans(data_3_fi[,6:15])

rowMeans(data_3_fi[,16:25])
data_3_fi$tr_NontargetedTrue1<-rowMeans(data_3_fi[,16:25])

rowMeans(data_3_fi[,26:35])
data_3_fi$tr_TargetedTrue<-rowMeans(data_3_fi[,26:35])

rowMeans(data_3_fi[,36:45])
data_3_fi$tr_NontargetedTrue2<-rowMeans(data_3_fi[,36:45])

#columns of self-report-TR for at
data_3_at$SelfReport_tr<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,90]<-(sum(data_3_at[i,c(49,50,51,53,56,57,58,59)]=="Strongly disagree")+2*sum(data_3_at[i,c(49,50,51,53,56,57,58,59)]=="Somewhat disagree")+3*sum(data_3_at[i,c(49,50,51,53,56,57,58,59)]=="Neither agree nor disagree")+4*sum(data_3_at[i,c(49,50,51,53,56,57,58,59)]=="Somewhat agree")+5*sum(data_3_at[i,c(49,50,51,53,56,57,58,59)]=="Strongly agree")+sum(data_3_at[i,c(52,54,55)]=="Strongly agree")+2*sum(data_3_at[i,c(52,54,55)]=="Somewhat agree")+3*sum(data_3_at[i,c(52,54,55)]=="Neither agree nor disagree")+4*sum(data_3_at[i,c(52,54,55)]=="Somewhat disagree")+5*sum(data_3_at[i,c(52,54,55)]=="Strongly disagree"))
}

#columns of self-report-TR for fi
data_3_fi$SelfReport_tr<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,90]<-(sum(data_3_fi[i,c(49,50,51,53,56,57,58,59)]=="Strongly disagree")+2*sum(data_3_fi[i,c(49,50,51,53,56,57,58,59)]=="Somewhat disagree")+3*sum(data_3_fi[i,c(49,50,51,53,56,57,58,59)]=="Neither agree nor disagree")+4*sum(data_3_fi[i,c(49,50,51,53,56,57,58,59)]=="Somewhat agree")+5*sum(data_3_fi[i,c(49,50,51,53,56,57,58,59)]=="Strongly agree")+sum(data_3_fi[i,c(52,54,55)]=="Strongly agree")+2*sum(data_3_fi[i,c(52,54,55)]=="Somewhat agree")+3*sum(data_3_fi[i,c(52,54,55)]=="Neither agree nor disagree")+4*sum(data_3_fi[i,c(52,54,55)]=="Somewhat disagree")+5*sum(data_3_fi[i,c(52,54,55)]=="Strongly disagree"))
}

#columns of confidence for at 
data_3_at$Confidence_life<-0
data_3_at$Confidence_exp<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,91]<-sum(data_3_at[i,47]=="None at all")+2*sum(data_3_at[i,47]=="A little")+3*sum(data_3_at[i,47]=="A moderate amount")+4*sum(data_3_at[i,47]=="A lot")+5*sum(data_3_at[i,47]=="A great deal")
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,92]<-sum(data_3_at[i,48]=="None at all")+2*sum(data_3_at[i,48]=="A little")+3*sum(data_3_at[i,48]=="A moderate amount")+4*sum(data_3_at[i,48]=="A lot")+5*sum(data_3_at[i,48]=="A great deal")
}

#columns of confidence for fi
data_3_fi$Confidence_life<-0
data_3_fi$Confidence_exp<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,91]<-sum(data_3_at[i,47]=="None at all")+2*sum(data_3_at[i,47]=="A little")+3*sum(data_3_at[i,47]=="A moderate amount")+4*sum(data_3_at[i,47]=="A lot")+5*sum(data_3_at[i,47]=="A great deal")
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,92]<-sum(data_3_at[i,48]=="None at all")+2*sum(data_3_at[i,48]=="A little")+3*sum(data_3_at[i,48]=="A moderate amount")+4*sum(data_3_at[i,48]=="A lot")+5*sum(data_3_at[i,48]=="A great deal")
}

#column of exhaustion for at 
data_3_at$exhaustion<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,93]<-sum(data_3_at[i,46]=="None at all")+2*sum(data_3_at[i,46]=="A little")+3*sum(data_3_at[i,46]=="A moderate amount")+4*sum(data_3_at[i,46]=="A lot")+5*sum(data_3_at[i,46]=="A great deal")
}

#column of exhaustion for fi 
data_3_fi$exhaustion<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,93]<-sum(data_3_at[i,46]=="None at all")+2*sum(data_3_at[i,46]=="A little")+3*sum(data_3_at[i,46]=="A moderate amount")+4*sum(data_3_at[i,46]=="A lot")+5*sum(data_3_at[i,46]=="A great deal")
}

#columns of news-consumption habits
data_3_at$media_attitude<-0
data_3_at$check_frequency<-0
data_3_at$sources<-0

for (i in 1:nrow(data_3_at)){
  data_3_at[i,94]<-sum(data_3_at[i,3]=="Almost never")+2*sum(data_3_at[i,3]=="Only some of the time")+3*sum(data_3_at[i,3]=="Most of the time")+4*sum(data_3_at[i,3]=="Just about always")
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,95]<-sum(data_3_at[i,4]=="Never")+2*sum(data_3_at[i,4]=="Once a week")+3*sum(data_3_at[i,4]=="3-4 times a week")+4*sum(data_3_at[i,4]=="Once a day")+5*sum(data_3_at[i,4]=="Multiple times a day")
}

for (i in 1:nrow(data_3_at)){
  data_3_at[i,96]<-sum(data_3_at[i,5]=="0")+2*sum(data_3_at[i,5]=="1")+3*sum(data_3_at[i,5]=="2")+4*sum(data_3_at[i,5]=="3")+5*sum(data_3_at[i,5]=="4")
}

#columns of news-consumption habits
data_3_fi$media_attitude<-0
data_3_fi$check_frequency<-0
data_3_fi$sources<-0

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,94]<-sum(data_3_fi[i,3]=="Almost never")+2*sum(data_3_fi[i,3]=="Only some of the time")+3*sum(data_3_fi[i,3]=="Most of the time")+4*sum(data_3_fi[i,3]=="Just about always")
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,95]<-sum(data_3_fi[i,4]=="Never")+2*sum(data_3_fi[i,4]=="Once a week")+3*sum(data_3_fi[i,4]=="3-4 times a week")+4*sum(data_3_fi[i,4]=="Once a day")+5*sum(data_3_fi[i,4]=="Multiple times a day")
}

for (i in 1:nrow(data_3_fi)){
  data_3_fi[i,96]<-sum(data_3_fi[i,5]=="0")+2*sum(data_3_fi[i,5]=="1")+3*sum(data_3_fi[i,5]=="2")+4*sum(data_3_fi[i,5]=="3")+5*sum(data_3_fi[i,5]=="4")
}

```

## Research question 1: investigate if and how differential exposure to misinformation affects individuals’ truth relativism towards true news
```{r pressure, echo=FALSE}
#compute the truth relativism of each headline and sequence them 
colMeans(data_3_at[,6:45])
dt3_headline<-data.frame(colMeans(data_3_at[,6:45]))

dt3_headline02<-data.frame(colMeans(data_3_fi[,6:45]))

#change the names of columns 
data_3_at<-data_3_at %>% 
  dplyr::rename("01" = "Q8.1_1", "02"="Q8.2_1",  "03"="Q8.3_1",                       
"04"="Q8.4_1",                            "05"="Q8.5_1",                          
"06"="Q8.7_1",                            "07"="Q8.8_1",                          
"08"="Q8.9_1",                           "09"="Q8.10_1",                         
"10"="Q8.11_1",                          "11"="Q8.12_1",                         
"12"="Q8.13_1",                         "13"="Q8.14_1",                        
"14"="Q8.16_1",                        "15"="Q8.17_1",                        
"16"="Q8.18_1",                       "17" ="Q8.19_1",                       
"18" ="Q8.20_1" ,                      "19" ="Q8.21_1",                      
"20" ="Q8.22_1",                     "21" ="Q9.1_1" ,                     
"22" ="Q9.2_1" ,                   "23" = "Q9.3_1",                    
"24"="Q9.4_1"  ,                   "25"="Q9.5_1"   ,                   
"26" = "Q9.6_1"     ,                 "27"=   "Q9.7_1"   ,                  
"28"="Q9.8_1"   ,                 "29" ="Q9.9_1"      ,                 
"30"="Q9.10_1"          ,               "31" = "Q9.11_1"     ,                
"32" ="Q9.12_1"         ,               "33"  = "Q9.13_1"   ,               
"34"  ="Q9.14_1"  ,              "35" ="Q9.15_1" ,              
"36"="Q9.16_1" ,             "37"= "Q9.17_1"          ,             
"38" ="Q9.18_1"       ,            "39"  ="Q9.19_1"       ,            
"40"="Q9.20_1")

data_3_fi<-data_3_fi %>% 
  dplyr::rename("01" = "Q6.1_2", "02"="Q6.2_1",  "03"="Q6.3_1",                       
"04"="Q6.4_1",                            "05"="Q6.5_1",                          
"06"="Q6.7_1",                            "07"="Q6.8_1",                          
"08"="Q6.9_1",                           "09"="Q6.10_1",                         
"10"="Q6.11_1",                          "11"="Q6.12_1",                         
"12"="Q6.13_1",                         "13"="Q6.14_1",                        
"14"="Q6.16_1",                        "15"="Q6.17_1",                        
"16"="Q6.18_1",                       "17" ="Q6.19_1",                       
"18" ="Q6.20_1" ,                      "19" ="Q6.21_1",                      
"20" ="Q6.22_1",                     "21" ="Q7.1_1" ,                     
"22" ="Q7.2_1" ,                   "23" = "Q7.3_1",                    
"24"="Q7.4_1"  ,                   "25"="Q7.5_1"   ,                   
"26" = "Q7.6_1"     ,                 "27"=   "Q7.7_1"   ,                  
"28"="Q7.8_1"   ,                 "29" ="Q7.9_1"      ,                 
"30"="Q7.10_1"          ,               "31" = "Q7.11_1"     ,                
"32" ="Q7.12_1"         ,               "33"  = "Q7.13_1"   ,               
"34"  ="Q7.14_1"  ,              "35" ="Q7.15_1" ,              
"36"="Q7.16_1" ,             "37"= "Q7.17_1"          ,             
"38" ="Q7.18_1"       ,            "39"  ="Q7.19_1"       ,            
"40"="Q7.20_1")
data_3_bind<-rbind(data_3_at,data_3_fi)

#Comparisons of truth relativism
#within all_true condition 
#Does targeting true news or targeted true news have higher truth relativism?
t.test(data_3_at$tr_Targeted,data_3_at$tr_TargetedTrue,paired=TRUE) 
mean(data_3_at$tr_Targeted)
mean(data_3_at$tr_TargetedTrue)
#visualisation regarding truth relativism
data_3_at_visualtr<-data_3_at[,c(2,63,86,87,88,89)] %>%
  pivot_longer(!c(ResponseId,condition), names_to = "subsets", values_to = "relativism_subsets")

#visualisation regarding accuracy(we chose 50 as correct for now because no difference was found between how we delat with 50 differently)
data_3_at_visualaccu<-data_3_at[,c(2,63,68,72,76,80)] %>%
  pivot_longer(!c(ResponseId,condition), names_to = "subsets", values_to = "accuracy_subsets")

data_3_at_visualaccu$subsets = substr(data_3_at_visualaccu$subsets,1,nchar(data_3_at_visualaccu$subsets)-11)

theme_apa <- function(base_size = 12, base_family = "", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(
      plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0), hjust = 0.5)
      , plot.subtitle = ggplot2::element_text(size = ggplot2::rel(0.8), margin = ggplot2::margin(ggplot2::rel(-7), 0, ggplot2::rel(14), 0), hjust = 0.5)

      # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
      , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
      , axis.title.x.top = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(12), 0))
      , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
      , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
      , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
      , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
      , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
      , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
      , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
      , axis.line = ggplot2::element_line()
      # , axis.line.x = ggplot2::element_line()
      # , axis.line.y = ggplot2::element_line()

      , legend.title = ggplot2::element_text()
      , legend.key = ggplot2::element_rect(fill = NA, color = NA)
      , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.margin = ggplot2::margin(
        t = ggplot2::rel(16)
        , r = ggplot2::rel(16)
        , b = ggplot2::rel(16)
        , l = ggplot2::rel(16)
        , unit = "points"
      )

      , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
      , panel.grid.major.x = ggplot2::element_blank()
      , panel.grid.minor.x = ggplot2::element_blank()
      , panel.grid.major.y = ggplot2::element_blank()
      , panel.grid.minor.y = ggplot2::element_blank()

      , strip.background = ggplot2::element_rect(fill = NA, color = NA)
      , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
      , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )

  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }

  adapted_theme
}

p_s3 <- ggplot(data_3_bind, aes(x=condition, y=tr_TargetedTrue)) + 
  labs(y="Truth Relativism of Targeted True News Headlines", x = "Treatment Group") +
  geom_boxplot(alpha=0.3,width = .15,outlier.shape = NA,fill="dark grey")+
  theme_classic()+
  geom_point(position = position_jitter(width = .15), size = 0.5,colour="black")+
  scale_x_discrete(labels = c('All True','Fake Included'))
p_s3
p_s3<-p_s3+theme_apa()
p_s3

#visualisation regarding truth relativism
data_3_fi_visualtr<-data_3_fi[,c(2,63,86,87,88,89)] %>%
  pivot_longer(!c(ResponseId,condition), names_to = "subsets", values_to = "relativism_subsets")

#visualisation regarding accuracy(we chose 50 as correct for now because no difference was found between how we delat with 50 differently)
data_3_fi_visualaccu<-data_3_fi[,c(2,63,68,72,76,80)] %>%
  pivot_longer(!c(ResponseId,condition), names_to = "subsets", values_to = "accuracy_subsets")

data_3_fi_visualaccu$subsets = substr(data_3_fi_visualaccu$subsets,1,nchar(data_3_fi_visualaccu$subsets)-11)

#between conditions 
#Does targeted true news in all_true condition have a lower truth_relativism compared with targeted true news in fake_included condition 
t.test(data_3_at$tr_TargetedTrue,data_3_fi$tr_TargetedTrue,paired=FALSE) 
aov_ez("ResponseId","tr_TargetedTrue",data_3_bind,between = "condition")

# Bayesian meta-analysis
#computing effect size 
aov_ez("ResponseId","tr_TargetedTrue",data_3_bind,between = "condition")

anova_model = lm(formula = tr_TargetedTrue ~ condition, data = data_3_bind)
summary.aov(anova_model)

library(MOTE)

eta.full.SS(dfm = 1, dfe = 83, ssm = 0.0039,
            sst = (0.0039+1.8089), Fvalue = 0.181, a = .05)

# Computing eta - outputs used in JASP
eta.full.SS(dfm = 1, dfe = 82, ssm = 148.173, sst = 1321000, Fvalue = 0.009, a = 0.05)

#Does Non-targeted true news in all_true condition have a different truth_relativism compared with nontargeted true news in fake_included condition 
t.test(data_3_at$tr_NontargetedTrue2,data_3_fi$tr_NontargetedTrue2,paired=FALSE)
mean(data_3_at$tr_NontargetedTrue2)
mean(data_3_fi$tr_NontargetedTrue2)

t.test(data_3_at$tr_NontargetedTrue1,data_3_fi$tr_NontargetedTrue1,paired=FALSE) 
mean(data_3_at$tr_NontargetedTrue2)
mean(data_3_fi$tr_NontargetedTrue2)
aov_ez("ResponseId","tr_NontargetedTrue2",data_3_bind,between = "condition")
aov_ez("ResponseId","tr_NontargetedTrue1",data_3_bind,between = "condition")

#Does targeting true news in all true condition have a different truth_relativism compared with targeting fake news in fake_included condition 
t.test(data_3_at$tr_Targeted,data_3_fi$tr_Targeted,paired=FALSE) 
aov_ez("ResponseId","tr_Targeted",data_3_bind,between = "condition")

aov_ez("ResponseId","tr_Targeted",data_3_bind,between = "condition")

#Does Non-targeted true news in all_true condition have a different accuracy compared with nontargeted true news in fake_included condition
t.test(data_3_at$accu_Targeted_50ascorrect,data_3_fi$accu_Targeted_50ascorrect,paired=FALSE) 

t.test(data_3_at$accu_Targeted_50aswrong,data_3_fi$accu_Targeted_50aswrong,paired=FALSE) 

t.test(data_3_at$accu_Targeted_50ashalf,data_3_fi$Targeted_50ashalf,paired=FALSE) 
aov_ez("ResponseId","accu_Targeted_50ascorrect",data_3_bind,between = "condition")

aov_ez("ResponseId","accu_Targeted_50ashalf",data_3_bind,between = "condition")

#Does accuracy of all decrease with the number of slider <50?
summary(lm(accu_all50ashalf~all_sliderlessthan50,data_3_bind)) 

#other accuracies
summary(lm(accu_TargetedTrue_50ashalf~all_sliderlessthan50,data_3_bind)) 

summary(lm(accu_Targeted_50ashalf~all_sliderlessthan50,data_3_bind)) 
summary(lm(accu_Targeted_50ashalf~all_sliderlessthan50,data_3_at)) 
summary(lm(accu_Targeted_50ashalf~all_sliderlessthan50,data_3_fi)) 


summary(lm(accu_NontargetedTrue1_50ashalf~all_sliderlessthan50,data_3_bind)) 



summary(lm(accu_TargetedTrue_50ashalf~all_sliderlessthan50,data_3_bind)) 
summary(lm(accu_TargetedTrue_50ashalf~all_sliderlessthan50,data_3_bind)) 
summary(lm(accu_NontargetedTrue2_50ashalf~all_sliderlessthan50,data_3_bind)) 
```

## Research question 2: examine whether differential exposure to misinformation affects individuals’ accuracy of judgements 
```{r}
# Does targeted true news in all_true condition have a higher accuracy compared with targeted true news in fake_included condition 
t.test(data_3_at$accu_TargetedTrue_50ascorrect,data_3_fi$accu_TargetedTrue_50ascorrect,paired=FALSE) 
mean(data_3_at$accu_TargetedTrue_50ascorrect)
mean(data_3_fi$accu_TargetedTrue_50ascorrect)
anova_accutargetedtrue<-aov_ez("ResponseId","accu_TargetedTrue_50ascorrect",data_3_bind,between = "condition")
anova_accutargetedtrue

t.test(data_3_at$accu_TargetedTrue_50aswrong,data_3_fi$accu_TargetedTrue_50aswrong,paired=FALSE) 
mean(data_3_at$accu_TargetedTrue_50aswrong)
mean(data_3_fi$accu_TargetedTrue_50aswrong)

t.test(data_3_at$accu_TargetedTrue_50ashalf,data_3_fi$accu_TargetedTrue_50ashalf,paired=FALSE) 
mean(data_3_at$accu_TargetedTrue_50ashalf)
mean(data_3_fi$accu_TargetedTrue_50ashalf)
aov_ez("ResponseId","accu_TargetedTrue_50ascorrect",data_3_bind,between = "condition")
aov_ez("ResponseId","accu_TargetedTrue_50ashalf",data_3_bind,between = "condition")

anova_model_accu = lm(formula = accu_TargetedTrue_50ascorrect ~ condition, data = data_3_bind)
summary.aov(anova_model_accu)

eta.full.SS(dfm = 1, dfe = 83, ssm = 0.0005,
            sst = (0.0039+1.4825), Fvalue = 0.03, a = .05)
```

#Analysis of how many pieces of news participants put the slider less than 50 
```{r}
#Is there a difference between how many pieces of news participants put the slider less than 50 of two conditions?
t.test(data_3_at$all_sliderlessthan50,data_3_fi$all_sliderlessthan50,paired=FALSE) 

anova_manipulation<-aov_ez("ResponseId","all_sliderlessthan50",data_3_bind,between = "condition")
anova_manipulation

emmeans(anova_manipulation,"condition")
```


##Research question 3: examine the correlation between truth relativism and individual’s self-reported relativism
```{r}
#TR and Self Report TR
summary(lm(tr_all~SelfReport_tr,data_3_bind))
cor.test(data_3_bind$tr_all,data_3_bind$SelfReport_tr)

anova_model_e3sr = lm(formula = SelfReport_tr ~ tr_all, data = data_3_bind)
summary.aov(anova_model_e3sr)

eta.full.SS(dfm = 1, dfe = 83, ssm = 0.4,
            sst = (0.4+1847.6), Fvalue = 0.016, a = .05)


summary(lm(tr_TargetedTrue~SelfReport_tr,data_3_bind))

summary(lm(tr_NontargetedTrue2~SelfReport_tr,data_3_bind))

summary(lm(tr_Targeted~SelfReport_tr,data_3_bind))

summary(lm(tr_NontargetedTrue1~SelfReport_tr,data_3_bind))
```

##Truth relativism and other factors
```{r}
#Confidence and TR
summary(lm(tr_all~Confidence_life,data_3_bind))
summary(lm(tr_all~Confidence_exp,data_3_bind))


#Exhaustion and TR
summary(lm(tr_all~exhaustion,data_3_bind))
cor.test(data_3_bind$tr_all,data_3_bind$exhaustion)


#Media consumption habits and TR
summary(lm(tr_all~media_attitude,data_3_bind))
summary(lm(tr_all~check_frequency,data_3_bind))
summary(lm(tr_all~check_frequency+media_attitude,data_3_bind))

summary(lm(tr_all~check_frequency+media_attitude+sources,data_3_bind))

summary(lm(tr_all~Q5.3,data_3_bind))
summary(lm(tr_all~sources,data_3_bind))

summary(lm(check_frequency~sources+media_attitude,data_3_bind))
summary(lm(check_frequency~sources,data_3_bind))
summary(lm(check_frequency~media_attitude,data_3_bind))


#tr_all and fake news experience(number of <50 rating)
summary(lm(tr_all~all_sliderlessthan50+all_numberof50,data_3_bind))


colnames(data_3_bind)
summary(lm(tr_all~accu_all50ashalf,data_3_bind)) 
summary(lm(tr_all~accu_all50aswrong,data_3_bind)) 
summary(lm(tr_all~accu_all50ascorrect,data_3_bind)) 

summary(lm(tr_TargetedTrue~accu_all50ashalf,data_3_bind)) 

aov_ez("ResponseId","tr_all",data_3_bind,between = "Q13.1")

ex<-aov_ez("ResponseId","exhaustion",data_3_bind,between = "condition")
ex

t.test(subset(data_3_bind, condition=="all_true")$"exhaustion", # because we have one measurement per person
       subset(data_3_bind, condition=="fake_include")$"exhaustion"
       )

afex_plot(ex,"condition",error = "between",mapping = "color")

tr_s3_ex<-emmeans(ex,"condition")
tr_s3_ex


```

